Event History Analyses for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2024-10-11 manuscript/manuscript.Rmd
add supplementary Material file

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "response times, event history analysis, Bayesian multi-level regression models, experimental psychology, cognitive psychology"
wordcount         : "X"
bibliography      : ["extrareferences.bib", "r-references.bib"]
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

@@

>>>>

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "response times, event history analysis, Bayesian multi-level regression models, experimental psychology, cognitive psychology"
wordcount         : "X"
bibliography      : ["extrareferences.bib", "r-references.bib"]
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
appendix          : SupplementaryMaterial.Rmd
output            : papaja::apa6_pdf

# output            : papaja::apa6_word
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

@@

```{r child = "SupplementaryMaterial.Rmd"}
```

### 2024-10-11 manuscript/manuscript.tex
add supplementary Material file

Integrating results between hazard and conditional accuracy functions can be informative for understanding psychological processes. To illustrate, we consider a hypothetical example that is inspired by real data (Panis et al., 2016), but simplified to make the main point clearer (Figure 3). In a standard stimulus-response-compatibility paradigm, there is a prime stimulus (e.g., a double arrow) followed by a target stimulus (single arrow). The prime can then be congruent or incongruent with the target. Taken together, the results show that for early responses (\textless{} bin 6), responses always follow the prime (and not the target, as instructed). And then for later responses, the prime can be overridden, as both conditions are now always correct. This is interesting because mean-average RT would only represent the overall ability of cognition to overcome interference, on average, across trials. And such a conclusion is not supporting when the effects are explored over a timeline. Instead, the psychological conclusion is much more nuanced and suggests that multiple states start, stop and possibly interact over a particular temporal window.

@@

>>>>

Integrating results between hazard and conditional accuracy functions can be informative for understanding psychological processes. To illustrate, we consider a hypothetical example that is inspired by real data (Panis et al., 2016), but simplified to make the main point clearer (Figure 3). In a standard response priming paradigm, there is a prime stimulus (e.g., an arrow pointing left or right) followed by a target stimulus (another arrow pointing left or right). The prime can then be congruent or incongruent with the target. Figure 3 shows that the early upswing in hazard is equal for both conditions, and that early responses are always correct in .. and always incorrect in the incongruent condtion. Taken together, the results show that for early responses (\textless{} bin 6), responses always follow the prime (and not the target, as instructed). And then for later bins, response hazard is lower in incongruent compared to congruent trials, as \ldots..the prime can be overridden, as both conditions are now always correct. This is interesting because mean-average RT would only represent the overall ability of cognition to overcome interference, on average, across trials. And such a conclusion is not supported when the effects are explored over a timeline. Instead, the psychological conclusion is much more nuanced and suggests that multiple states start, stop and possibly interact over a particular temporal window.

@@

\section{Supplementary Material}\label{supplementary-material}

here is the supp
